SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v21]

### 2015-09-11 paper.tex
updated teaser photo

\includegraphics[width=0.5\textwidth]{figures/teaser.pdf}
\caption{ 
SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) cost of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
}
\vspace*{-10pt}
\label{fig:teaser}
\end{figure}

>>>>

\includegraphics[width=0.5\textwidth]{figures/teaser.pdf}
\caption{ 
SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
}
\vspace*{-10pt}
\label{fig:teaser}
\end{figure}
